Modified replication

### 2020-06-06 rep_nosmooth/README.Rmd

In order to be able to run the models needed to create tables 1 and 2 more quickly than with the original replication code, the code here has been re-factored to enable running in parallel. Here is a summary of the major changes:

- `re-save-data.R` changes the format of the saved 1-month and 6-month data versions from Stata 13 .dta files to R .rds format. This can be read much quicker than the Stata format. 
- `setup-model-table.R` encodes all the various pieces of information needed to actually run the models reflected in tables 1 and 2. In the original replication files this is done in bits and pieces in `+master.R`, `code/[1|6]mo_define_models.R`, and each model runner file, e.g. `code/1mo_run_escalation.R`. The primary output are several files written to the `output/model-definitions` folder. More details on this below.
- `model-runner.R` runs the models. Adjust the number of WORKERS at the top of the script as needed based on the number of cores on your computer. The primary output of this script is `output/model-table-w-results.csv` and `output/all-predictions.R`.
- `recreate-tables.R` recreates the original and non-smooth ROC versions of Tables 1 and 2 using `output/model-table-w-results.csv` and `output/all-predictions.R`.

@@

- [variance.md](/variance.md) examines how much the AUC-ROC results vary when you don't set an RNG seed. For the base specification escalation model, the variance is significantly below 0.01, and small changes in the Table 1 and 2 replications mainly occur when the distribution straddles a threshold used for rounding, e.g. 0.825. 
- `make-original-tables.R` is a by-hand coding of the values reported for Tables 1, 2, and 4 in B&S 2020.

### Model definitions

>>>>

In order to be able to run the models needed to create tables 1 and 2 more quickly than with the original replication code, the code here has been re-factored to enable running in parallel. The structure of the code has completely changed. Instead of a master script that handles file IO and sources other scripts to setup model definition objects (features, training/test data frames, etc.) and run models, the new logic is to:

1. Create a central model table that encodes all cells in B&S Tables 1 and 2 and the information needed to define the underlying models, as well as associated model definitions like features, hyper-parameter settings, etc. (`output/model-definitions/`). 
2. Run through the model table (mostly in parallel) to estimate all models; save the resulting predictions. 
3. Re-create output tables and figures.

## (Clean) replication

Below are instructions for how to run the script in order to replicate the updated analysis. To do a clean replication, delete the `output/` folder; this is not required though.

Run through the files in the following order:

- `re-save-data.R` changes the format of the saved 1-month and 6-month data versions from Stata 13 .dta files to R .rds format. This can be read much quicker than the Stata format. 
- `setup-model-table.R` encodes all the various pieces of information needed to actually run the models reflected in tables 1 and 2. In the original replication files this is done in bits and pieces in `+master.R`, `code/[1|6]mo_define_models.R`, and each model runner file, e.g. `code/1mo_run_escalation.R`. The primary output are several files written to the `output/model-definitions` folder. More details on this below.
- `model-runner.R` runs the models. Adjust the number of WORKERS at the top of the script as needed based on the number of cores on your computer. The primary output of this script is `output/model-table-w-results.csv` and `output/all-predictions.R`.
- `recreate-tables.R` recreates the original and non-smooth ROC versions of Tables 1 and 2 using `output/model-table-w-results.csv` and `output/all-predictions.R`.
- `recreate-figure1.R` recreates the ROC curves in B&S Figure 1 using `output/model-table-w-results.csv` and `output/all-predictions.R`.

@@

- [variance.md](variance.md) examines how much the AUC-ROC results vary when you don't set an RNG seed. For the base specification escalation model, the variance is significantly below 0.01, and small changes in the Table 1 and 2 replications mainly occur when the distribution straddles a threshold used for rounding, e.g. 0.825. 
- `make-original-tables.R` is a by-hand coding of the values reported for Tables 1, 2, and 4 in B&S 2020.

## Model definitions
